Total Amount of Vaccinations by Gender Among Black population in the Target Zip Codes

### 2023-04-06 code/analysis_code/analysiscode2.qmd
Part 4

#### Using the select() function to subset the data frame by columns that start with "total_black_vax" which are variables with a total count of Black population with at least one dose of the COVID-19 vaccine by month

@@

### Summing each Month variable by census tract
```{r}
#Summing for black males by month 
sum(processed_combined_31701_total_black$total_mblack_vax_Sept_17) 
sum(processed_combined_31701_total_black$total_mblack_vax_Oct_28) 
sum(processed_combined_31701_total_black$total_mblack_vax_Nov_24) 
sum(processed_combined_31701_total_black$total_mblack_vax_Dec_29) 
sum(processed_combined_31701_total_black$total_mblack_vax_Jan_26) 
sum(processed_combined_31701_total_black$total_mblack_vax_Feb_26)

#summing for black females by month 
sum(processed_combined_31701_total_black$total_fblack_vax_Sept_17) 
sum(processed_combined_31701_total_black$total_fblack_vax_Oct_28) 
sum(processed_combined_31701_total_black$total_fblack_vax_Nov_24) 
sum(processed_combined_31701_total_black$total_fblack_vax_Dec_29) 
sum(processed_combined_31701_total_black$total_fblack_vax_Jan_26) 
sum(processed_combined_31701_total_black$total_fblack_vax_Feb_26) 
```

@@

```{r}
plot_Gender_black_vax = Gender_Sum_by_month_31701_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Gender, 
                                color = Gender)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Total_black_vax = plot_Total_black_vax + 
  ggtitle("Vaccination Totals for Black population by Gender in 31701") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Gender_black_vax
```

@@

#### Using the select() function to subset the data frame by columns that start with "total_black_vax" which are variables with a total count of Black population with at least one dose of the COVID-19 vaccine by month

```{r}
processed_combined_31705_total_black = processed_combined_31705 %>% select(matches("^total_(mblack|fblack)_vax"))
```

### Summing each Month variable by census tract
```{r}
#Summing for black males by month 
sum(processed_combined_31705_total_black$total_mblack_vax_Sept_17) 
sum(processed_combined_31705_total_black$total_mblack_vax_Oct_28) 
sum(processed_combined_31705_total_black$total_mblack_vax_Nov_24) 
sum(processed_combined_31705_total_black$total_mblack_vax_Dec_29) 
sum(processed_combined_31705_total_black$total_mblack_vax_Jan_26) 
sum(processed_combined_31705_total_black$total_mblack_vax_Feb_26)

#summing for black females by month 
sum(processed_combined_31705_total_black$total_fblack_vax_Sept_17) 
sum(processed_combined_31705_total_black$total_fblack_vax_Oct_28) 
sum(processed_combined_31705_total_black$total_fblack_vax_Nov_24) 
sum(processed_combined_31705_total_black$total_fblack_vax_Dec_29) 
sum(processed_combined_31705_total_black$total_fblack_vax_Jan_26) 
sum(processed_combined_31705_total_black$total_fblack_vax_Feb_26) 
```

@@

```{r}
plot_Gender_black_vax_31705 = Gender_Sum_by_month_31705_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Gender, 
                                color = Gender)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Total_black_vax = plot_Total_black_vax + 
  ggtitle("Vaccination Totals for Black population by Gender in 31705") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Gender_black_vax_31705
```

@@

#### Using the select() function to subset the data frame by columns that start with "total_black_vax" which are variables with a total count of Black population with at least one dose of the COVID-19 vaccine by month

```{r}
processed_combined_31707_total_black = processed_combined_31707 %>% select(matches("^total_(mblack|fblack)_vax"))
```

### Summing each Month variable by census tract
```{r}
#Summing for black males by month 
sum(processed_combined_31707_total_black$total_mblack_vax_Sept_17) 
sum(processed_combined_31707_total_black$total_mblack_vax_Oct_28) 
sum(processed_combined_31707_total_black$total_mblack_vax_Nov_24) 
sum(processed_combined_31707_total_black$total_mblack_vax_Dec_29) 
sum(processed_combined_31707_total_black$total_mblack_vax_Jan_26) 
sum(processed_combined_31707_total_black$total_mblack_vax_Feb_26)

#summing for black females by month 
sum(processed_combined_31707_total_black$total_fblack_vax_Sept_17) 
sum(processed_combined_31707_total_black$total_fblack_vax_Oct_28) 
sum(processed_combined_31707_total_black$total_fblack_vax_Nov_24) 
sum(processed_combined_31707_total_black$total_fblack_vax_Dec_29) 
sum(processed_combined_31707_total_black$total_fblack_vax_Jan_26) 
sum(processed_combined_31707_total_black$total_fblack_vax_Feb_26) 
```

@@

```{r}
plot_Gender_black_vax_31707 = Gender_Sum_by_month_31707_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Gender, 
                                color = Gender)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Total_black_vax = plot_Total_black_vax + 
  ggtitle("Vaccination Totals for Black population by Gender in 31707") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Gender_black_vax_31707
```

>>>>

#### Using the select() function to subset the data frame by columns that start with "Gender_black_vax" which are variables with a total count of Black population with at least one dose of the COVID-19 vaccine by month

@@

### Summing each Month variable by census tract
```{r}
#Summing for black males by month 
sum(processed_combined_31701_Gender_black$total_mblack_vax_Sept_17) 
sum(processed_combined_31701_Gender_black$total_mblack_vax_Oct_28) 
sum(processed_combined_31701_Gender_black$total_mblack_vax_Nov_24) 
sum(processed_combined_31701_Gender_black$total_mblack_vax_Dec_29) 
sum(processed_combined_31701_Gender_black$total_mblack_vax_Jan_26) 
sum(processed_combined_31701_Gender_black$total_mblack_vax_Feb_26)

#summing for black females by month 
sum(processed_combined_31701_Gender_black$total_fblack_vax_Sept_17) 
sum(processed_combined_31701_Gender_black$total_fblack_vax_Oct_28) 
sum(processed_combined_31701_Gender_black$total_fblack_vax_Nov_24) 
sum(processed_combined_31701_Gender_black$total_fblack_vax_Dec_29) 
sum(processed_combined_31701_Gender_black$total_fblack_vax_Jan_26) 
sum(processed_combined_31701_Gender_black$total_fblack_vax_Feb_26) 
```

@@

```{r}
plot_Gender_black_vax = Gender_Sum_by_month_31701_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Gender, 
                                color = Gender)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Gender_black_vax = plot_Gender_black_vax + 
  ggtitle("Vaccination Totals for Black population by Gender in 31701") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Gender_black_vax
```

@@

#### Using the select() function to subset the data frame by columns that start with "Gender_black_vax" which are variables with a total count of Black population with at least one dose of the COVID-19 vaccine by month

```{r}
processed_combined_31705_Gender_black = processed_combined_31705 %>% select(matches("^total_(mblack|fblack)_vax"))
```

### Summing each Month variable by census tract
```{r}
#Summing for black males by month 
sum(processed_combined_31705_Gender_black$total_mblack_vax_Sept_17) 
sum(processed_combined_31705_Gender_black$total_mblack_vax_Oct_28) 
sum(processed_combined_31705_Gender_black$total_mblack_vax_Nov_24) 
sum(processed_combined_31705_Gender_black$total_mblack_vax_Dec_29) 
sum(processed_combined_31705_Gender_black$total_mblack_vax_Jan_26) 
sum(processed_combined_31705_Gender_black$total_mblack_vax_Feb_26)

#summing for black females by month 
sum(processed_combined_31705_Gender_black$total_fblack_vax_Sept_17) 
sum(processed_combined_31705_Gender_black$total_fblack_vax_Oct_28) 
sum(processed_combined_31705_Gender_black$total_fblack_vax_Nov_24) 
sum(processed_combined_31705_Gender_black$total_fblack_vax_Dec_29) 
sum(processed_combined_31705_Gender_black$total_fblack_vax_Jan_26) 
sum(processed_combined_31705_Gender_black$total_fblack_vax_Feb_26) 
```

@@

```{r}
plot_Gender_black_vax_31705 = Gender_Sum_by_month_31705_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Gender, 
                                color = Gender)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Gender_black_vax = plot_Gender_black_vax + 
  ggtitle("Vaccination Totals for Black population by Gender in 31705") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Gender_black_vax_31705
```

@@

#### Using the select() function to subset the data frame by columns that start with "Gender_black_vax" which are variables with a total count of Black population with at least one dose of the COVID-19 vaccine by month

```{r}
processed_combined_31707_Gender_black = processed_combined_31707 %>% select(matches("^total_(mblack|fblack)_vax"))
```

### Summing each Month variable by census tract
```{r}
#Summing for black males by month 
sum(processed_combined_31707_Gender_black$total_mblack_vax_Sept_17) 
sum(processed_combined_31707_Gender_black$total_mblack_vax_Oct_28) 
sum(processed_combined_31707_Gender_black$total_mblack_vax_Nov_24) 
sum(processed_combined_31707_Gender_black$total_mblack_vax_Dec_29) 
sum(processed_combined_31707_Gender_black$total_mblack_vax_Jan_26) 
sum(processed_combined_31707_Gender_black$total_mblack_vax_Feb_26)

#summing for black females by month 
sum(processed_combined_31707_Gender_black$total_fblack_vax_Sept_17) 
sum(processed_combined_31707_Gender_black$total_fblack_vax_Oct_28) 
sum(processed_combined_31707_Gender_black$total_fblack_vax_Nov_24) 
sum(processed_combined_31707_Gender_black$total_fblack_vax_Dec_29) 
sum(processed_combined_31707_Gender_black$total_fblack_vax_Jan_26) 
sum(processed_combined_31707_Gender_black$total_fblack_vax_Feb_26) 
```

@@

```{r}
plot_Gender_black_vax_31707 = Gender_Sum_by_month_31707_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Gender, 
                                color = Gender)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Gender_black_vax = plot_Gender_black_vax + 
  ggtitle("Vaccination Totals for Black population by Gender in 31707") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Gender_black_vax_31707
```
